---
title: "final"
author: "Chandrasekhar Gudipati"
date: "11/4/2020"
output:
  html_document:
    df_print: paged
runtime: shiny
---
I'll now show you my work of grandeur. The first thing is that this has twoo parrts. Chandrasekhar's Server and Chandrasekhar's UI. I then take the two to make Chandrasekhar's Shiny app. This file has both and how I fused them for Chandrasekhar's app.
This is the link for my app btw:
https://cgudipati.shinyapps.io/Submission/
Do enjoy!!!!!

### Chandrasekhar's Server Side
```{r}
library(plotly)
library(shiny)
mdc <- mtcars
mdc$am <- factor(mdc$am, labels = c("Automatic", "Manual"))
shinyServer(function(input, output) {
  
  ftc <- reactive({
    paste("Milespgc vs ", input$variable)
  })
  
  output$caption <- renderText({
    ftc()
  })
  output$mpgPlot <- renderPlot({
    ggplot(mdc, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```
###Chandrasekhar's UI Side
```{r}
library(shiny)
shinyUI(fluidPage(
  
  titlePanel("Chandrasekhar's Dataset - Miles per Gallon"),
  
  sidebarPanel(
    
    selectInput("variable", "Variable:", 
                c("Chandrasekhar's Cyl" = "cyl",
                  "Chandrasekhar's Automatic" = "am",
                  "Gears of Chandrasekhar" = "gear"))
  ),
  
  mainPanel(
    h2(textOutput("caption")),
    # Welcome to Chandrasekhar's Graph app.

    plotOutput("mpgPlot")
  )
))
```
Et voila!!!! You have just witnessed Chandrasekhar's Shiny app presentation!!!